\textbf{Unshuffling Permutations}

### 2016-04-06 slides/slides.tex
(co)products

\usepackage{euler,palatino}
\usepackage{amsmath,amssymb}
\usepackage[utf8]{inputenc}
\usepackage{xxcolor}
\usepackage{graphicx}
\usepackage[ruled]{algorithm2e}
\usepackage[english]{babel}
\usepackage{rotate}
\usepackage{shuffle}
\usepackage{minted}
\usepackage{url}
\usepackage{etoolbox}
\usepackage{tikz}
\usepackage{rotating}
\usetikzlibrary{snakes}
\usetikzlibrary{trees}
\usetikzlibrary{arrows}
\usetikzlibrary{matrix}
\usetikzlibrary{calc}

@@

@@

>>>>

\usepackage{euler,palatino}
\usepackage{amsmath,amssymb}
\usepackage[utf8]{inputenc}
\usepackage{xxcolor}
\usepackage{graphicx}
\usepackage[ruled]{algorithm2e}
\usepackage[english]{babel}
\usepackage{rotate}
\usepackage{shuffle}
%\usepackage{minted}
\usepackage{url}
\usepackage{etoolbox}
\usepackage{tikz}
\usepackage{rotating}
\usetikzlibrary{snakes}
\usetikzlibrary{trees}
\usetikzlibrary{arrows}
\usetikzlibrary{matrix}
\usetikzlibrary{calc}

@@

\DeclareMathOperator{\QQ}{\mathbb{Q}}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame} \frametitle{Combinatorial products and structure coefficients}
Let $C$ be a set of combinatorial objects and let $\QQ[C]$ be the
$\QQ$-linear span of $C$.
\medskip

A binary linear product
\begin{equation*}
    \cdot : \QQ[C] \otimes \QQ[C] \to \QQ[C].
\end{equation*}
on $\QQ[C]$ describes a way to \alert{combine} two objects of
$C$ to obtain \alert{bigger} objects.
\medskip

In a general way, for any $x, y \in C$,
\begin{equation*}
    x \cdot y = \sum_{z \in C} \lambda_{x, y}^z \; z.
\end{equation*}

A product is wholly encoded by the coefficients
$\lambda_{x, y}^z \in \QQ$, $x, y, z \in C$, called
\alert{structure coefficients}.
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame} \frametitle{Combinatorial coproducts}
In a dual way, a linear coproduct
\begin{equation*}
    \Delta : \QQ[C] \to \QQ[C] \otimes \QQ[C].
\end{equation*}
on $\QQ[C]$ describe a way to \alert{break} one object of $C$ into
\alert{two smaller} pieces.
\medskip

In a general way, for any $z \in C$,
\begin{equation*}
    \Delta(x) = \sum_{x, y \in C}  \lambda_{x, y}^z \;  x \otimes y.
\end{equation*}

A coproduct is wholly encoded by the coefficients
$\lambda_{x, y}^z \in \QQ$, $x, y, z \in C$, called
\alert{structure coefficients}.
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame} \frametitle{Equivalence between products and coproducts}
If $\cdot : \QQ[C] \otimes \QQ[C] \to \QQ[C]$ is a product with
structure coefficients $\lambda_{x, y}^z \in \QQ$, $x, y, z \in C$,
we can define its \alert{dual coproduct} $\Delta$ by setting
\begin{equation*}
    \Delta(x) := \sum_{x, y \in C}  \lambda_{x, y}^z \;  x \otimes y.
\end{equation*}
\medskip

Conversely, if $\Delta : \QQ[C] \to \QQ[C] \otimes \QQ[C]$ is
a coproduct with structure coefficients $\lambda_{x, y}^z \in \QQ$,
$x, y, z \in C$, we can define its \alert{dual product} $\cdot$ by
setting
\begin{equation*}
    x \cdot y := \sum_{z \in C} \lambda_{x, y}^z \; z.
\end{equation*}

\begin{block}{Idea}
    Knowing how to break a combinatorial object is equivalent
    to knowing how to combine these.
\end{block}
\end{frame}
